logbook simulations

### 2020-03-23 datasets/data_preprocessing.nb.Rmd
- add virus dataset - update simulation log

@@

# hall
write.csv(hall_test, "test_datasets/software.csv")
# wilson
write.csv(w_test, "test_datasets/wilson.csv")

>>>>

## Virus dataset
```{r}
v_raw <- read.csv("../../sims/data/virus.csv")

sum(v_raw$abstract == "")

v_test <- v_raw %>%
  drop_na(abstract) %>%
  filter(abstract != "", abstract != "NA")

v_test <- v_test[v_test$record_id != 1732,]

@@

# hall
write.csv(hall_test, "test_datasets/software.csv")

# virus 
write.csv(v_test, "test_datasets/virus.csv")

# wilson
write.csv(w_test, "test_datasets/wilson.csv")

### 2020-03-23 simulation/README.Rmd
- add virus dataset - update simulation log

### extract simulation results nb 
```{bash}
# transfer files to device 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output
```

@@

```{bash, eval = FALSE}
./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/results_ace.h5" -r 23 
./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/results_nudging.h5" -r 23 
./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/results_ptsd.h5" -r 23 
./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/results_software.h5" -r 23 
./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/results_wilson.h5" -r 23 
```

Process BCTW models into table
 - python script to extract statistics
 -

@@

(re)Simulate BCTW models 
Simulate SCTW models

@@

>>>>

### extract simulation results nb 
```{bash}
# transfer files to device 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output

scp -r /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/hyperopt/config/one gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config
```

@@

@@

(re)Simulate BCTW models

```{bash, eval = FALSE}
./cart_simulate.py data/ace.csv --config_file config/one/BCTW_ace.ini --state_file "simoutput/bctw/ace/results_ace.h5" -r 23 # 7814382
./cart_simulate.py data/nudging.csv --config_file config/one/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/results_nudging.h5" -r 23 # 7814384
./cart_simulate.py data/ptsd.csv --config_file config/one/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/results_ptsd.h5" -r 23 # 7814391
./cart_simulate.py data/software.csv --config_file config/one/BCTW_software.ini --state_file "simoutput/bctw/software/results_software.h5" -r 23 # 7814392 
./cart_simulate.py data/wilson.csv --config_file config/one/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/results_wilson.h5" -r 23 # 7814395
```

@@

Process BCTW models into table
 - python script to extract statistics

Checkout what happened with NCDW and other errors in hpcbatch

Simulate SCTW models
